---
title: "Prix de vente de maisons à King County"
author: "Matis Brassard-Verrier, Alyson Marquis, Alexis Picard et Samuel Provencher"
output:
     powerpoint_presentation:
        reference_doc : Présentation1.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Bibliographie

1. Kaggle, harlfoxen (2017). House sales in King County, USA. Récupéré le 27 février 2020 de https://www.kaggle.com/harlfoxem/housesalesprediction.
\newline
2. Max Kuhn (2020). caret: Classification and Regression Training. R package version 6.0-85. https://CRAN.R-project.org/package=caret
\newline
3. Terry Therneau and Beth Atkinson (2019). rpart: Recursive Partitioning and Regression Trees. R package version 4.1-15. https://CRAN.R-project.org/package=rpart
\newline
4. Stephen Milborrow (2019). rpart.plot: Plot 'rpart' Models: An Enhanced Version of 'plot.rpart'. R package version 3.0.8. https://CRAN.R-project.org/package=rpart.plot

## Bibliographie

5. A. Liaw and M. Wiener (2002). Classification and Regression by randomForest. R News 2(3), 18--22.
\newline
6. Brandon Greenwell, Bradley Boehmke, Jay Cunningham and GBM Developers (2019). gbm: Generalized Boosted Regression Models. R package version 2.1.5. https://CRAN.R-project.org/package=gbm
\newline
7. Jerome Friedman, Trevor Hastie, Robert Tibshirani (2010). Regularization Paths for Generalized Linear Models via Coordinate Descent. Journal of Statistical Software, 33(1), 1-22. URL http://www.jstatsoft.org/v33/i01/.
\newline
8. Alina Beygelzimer, Sham Kakadet, John Langford, Sunil Arya, David Mount and Shengqiao Li (2019). FNN: Fast Nearest Neighbor Search Algorithms and Applications. R package
version 1.1.3.  https://CRAN.R-project.org/package=FNN
